\documentclass[11pt]{article}
\usepackage[margin=0.85in]{geometry}
\usepackage{booktabs,longtable,hyperref}
\title{GoalOS-native alpha-AGI Ascension using AGIALPHA\\\large Sovereign RSI Architecture for Proof-Governed Intelligence Organizations}
\author{Vincent Boucher\\President, QUEBEC.AI \& MONTREAL.AI}
\date{Corporate Sovereign RSI Edition v6.1}
\begin{document}
\maketitle
\begin{abstract}
AI-first institutions should not merely automate work; they should generate evidence sufficient to govern what may improve next. This paper presents GoalOS-native alpha-AGI Ascension using AGIALPHA: a sovereign RSI architecture in which institutional aims become commitments, agent work becomes ProofBundles, reviewers produce attestations, the Proof Gradient selects only evidence-backed upgrades, and Evidence Dockets make claims auditable. AGIALPHA is treated as a utility coordination asset for proof-settled work: mission posting, bonds, reviewer accountability, settlement, proof-card actions, credentials, reputation and access. The paper does not claim achieved AGI, superintelligence, guaranteed financial return or deployment authorization. It defines the institutional machinery required to test whether useful AI workflow work can become governed, reusable, compounding capability.
\end{abstract}
\section*{Core thesis}
GoalOS sets the aim. AGIALPHA coordinates proof-settled work. AEP-001 defines valid evidence. The Proof Gradient decides what may evolve. The Artifact Vault stores reusable intelligence. The Run Fabric executes bounded agents. The Proof Ledger records what happened. The Selection Gate promotes only what survived evidence. The Chronicle preserves institutional memory. The intelligence stays private. The proof becomes verifiable. The network improves only through verified work.
\section*{Claim boundary}
This paper defines a research architecture, implementation direction and evidence program. It does not authorize deployment or guarantee outcomes.
\end{document}
