\documentclass[11pt]{article}
\usepackage[margin=0.85in]{geometry}
\usepackage{booktabs,longtable,array,xcolor,hyperref,graphicx}
\definecolor{ink}{HTML}{071323}
\definecolor{gold}{HTML}{B7892A}
\title{GoalOS-Native alpha-AGI Ascension using AGIALPHA\\A Sovereign RSI Architecture for Evidence-Governed Intelligence Organizations}
\author{Vincent Boucher\\President, QUEBEC.AI \& MONTREAL.AI}
\date{Sovereign RSI Edition v6.3}
\begin{document}\maketitle
\section*{Abstract}
AI systems should not merely act, remember, or self-improve. They should produce evidence strong enough to govern what may improve next. GoalOS-native alpha-AGI Ascension using AGIALPHA defines a sovereign RSI architecture in which institutional aims become signed commitments, bounded agents execute proof missions, AGIALPHA coordinates proof-settled work, reviewers validate evidence, Evidence Dockets make claims auditable, and the Selection Gate grants propagation rights only to verified improvements.
\section*{Core thesis}
GoalOS sets sovereign aims. AGIALPHA coordinates proof-settled work. AEP-001 defines valid evidence. The Proof Gradient decides what may evolve. The intelligence stays private. The proof becomes verifiable.
\section*{Selection law}
\[ Promote(u)=1 \iff Proof(u) \land EvalPass(u) \land RiskOK(u) \land ScopeOK(u) \land CanaryOK(u) \land MonitorOK(u) \land RollbackReady(u). \]
\section*{Claim boundary}
This document is a protocol and architecture paper, not a mainnet authorization, legal opinion, tax opinion, security certification, or investment document.
\end{document}
